\chapter{Getting Started}

Follow these steps to start using the Zero Drift DDM GUI effectively.

\section{Launching the GUI}
\begin{enumerate}
    \item Open MATLAB and ensure the GUI folder is added to the MATLAB path.
    \item Launch the GUI using one of the methods outlined in the \textbf{Installation} section.
\end{enumerate}

\section{Understanding the Interface}
The GUI consists of:
\begin{itemize}
    \item \textbf{Main Settings Panel:} Configure simulation parameters (e.g., block number, choice number).
    \item \textbf{Visualization Area:} Displays dynamic plots, decision time distributions, and reward rate distributions.
    \item \textbf{Interactive Elements:} Buttons, sliders, and menus to control simulations.
    \item \textbf{Menu Bar:} Options for exporting figures for saving or further interaction, including features for saving 3D plots.
\end{itemize}

\section{Running Your First Simulation}
\begin{enumerate}
    \item With the GUI open, verify the default settings are loaded.
    \item Click \textbf{Run Simulation} to execute a test simulation.
    \item Observe the outputs, including:
    \begin{itemize}
        \item \textbf{Random Walk Plot:} Displays the decision process.
        \item \textbf{Dynamic Plot:} Shows evolving reward rates and thresholds.
        \item \textbf{Choice Proportion Plot:} Summarizes decision patterns.
    \end{itemize}
\end{enumerate}

\section{Saving Results}
\begin{enumerate}
    \item Use the \textbf{File} menu to select \textbf{Save Results}.
    \item Choose a directory and confirm the file is saved as a \texttt{.mat}.
\end{enumerate}

\section{Exploring Advanced Features}
\begin{itemize}
    \item Enable batch simulations using the checkbox in the settings panel.
    \item Customize parameters like cost models and decision thresholds.
    \item Use the \textbf{Import Data} tab to analyze pre-simulated datasets.
\end{itemize}

\section{Tips for Beginners}
\begin{itemize}
    \item Start with simple settings to learn the interface.
    \item Access the \hyperref[ch:functionality]{Functionality} section for parameter explanations.
    \item Save configurations frequently.
\end{itemize}

With these steps, you're ready to explore the Zero Drift DDM GUI. Happy simulating!