\chapter{Installation}

\section{Install MATLAB}
\begin{enumerate}
    \item Visit \url{https://www.mathworks.com} to purchase, download, and install MATLAB.
    \item Ensure the following toolbox is installed and licensed:
    \begin{itemize}
        \item \textbf{Statistics and Machine Learning Toolbox}
    \end{itemize}
\end{enumerate}

\section{Download and Extract the GUI}
\begin{enumerate}
    \item Obtain the GUI files from the designated source (e.g., GitHub or an institutional website).
    \item If the files are compressed in a \texttt{.zip}, extract them to your desired directory.
    \item Verify that all required files (e.g., \texttt{.m} and \texttt{.mlapp} files) are intact.
\end{enumerate}

\section{Add the GUI Folder to MATLAB Path}
\begin{enumerate}
    \item Open MATLAB.
    \item Navigate to the \textbf{Home} tab and select \textbf{Set Path}.
    \item Click \textbf{Add Folder} and select the directory containing the GUI files.
    \item Click \textbf{Save} to finalize the path addition.
\end{enumerate}

\section{Run the GUI}
You can launch the GUI in two ways:
\begin{enumerate}
    \item Open MATLAB, type the following command in the Command Window, and press \textbf{Enter}:
    \begin{verbatim}
    ZeroDriftDDM2
    \end{verbatim}
    \item Alternatively, locate the \texttt{ZeroDriftDDM2.mlapp} file in your file explorer (Finder for macOS or File Explorer for Windows) and double-click it to open. 
    \begin{itemize}
        \item Note: Before using this method, ensure MATLAB is open and the GUI folder is correctly added to the path to prevent potential bugs.
    \end{itemize}
\end{enumerate}

\section{Verify Installation}
\begin{enumerate}
    \item Launch the GUI and run a test simulation with default settings.
    \item Confirm that plots and interactive elements function as expected.
\end{enumerate}

\section{Troubleshooting}
\begin{itemize}
    \item If the GUI fails to launch, verify the folder is added to the MATLAB path.
    \item Ensure all required toolboxes are installed and licensed.
    \item Consult the \textbf{Support} section for additional help.
\end{itemize}